Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-19 RET_Hosts.tex

@@

Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}. In order to test this possibility, we examined the RETs that do not have a host galaxy redshift. Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process. Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}. Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign. The other, `hostless', objects are either transients that are located remotely from a host that was detected, or are hosted by a galaxy that was not detected. Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both. Neither are expected to be systematically higher in metallicity than the detected hosts. Similarly, a further 16 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found. The resulting redshift completeness of targetted objects is 70\% (82\% for objects brighter than $m_r = 24$~mag, which is in line with the average for OzDES as a whole \citep{Lidman2020}.
In Fig. \ref{fig:g-r} we show the observer-frame $i$-band magnitudes and $g-r$ colours for all RET hosts that were detected. The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts. This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
\label{fig:g-i}}
\end{figure}

@@

Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}. In order to test this possibility, we examined the RETs that do not have a host galaxy redshift. Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process. Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}. Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign. The other, `hostless', objects are either transients that are located remotely from a host that was detected, or are hosted by a galaxy that was not detected. Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both. Neither are expected to be systematically higher in metallicity than the detected hosts. Similarly, a further 16 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found. The resulting redshift completeness of targetted objects is 70\% (82\% for objects brighter than $m_r = 24$~mag, which is in line with the average for OzDES as a whole \citep{Lidman2020}.
In Fig. \ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected. The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts. This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.
